An open reproducible framework for the study of the iterated prisoner's dilemma

### 2016-03-11 tex/paper.tex
Adding high school contributions.

To date the library has had contributions from 24 contributors from a variety
of backgrounds. These contributions have both been in terms of strategies (one
strategy is the creation of an undergraduate mathematics student with little
prior knowledge of programming) as well as the architecture of the library
itself. You can see an overview of the structure of the source code in
Figure~\ref{fig:overview}.

>>>>

To date the library has had contributions from 24 contributors from a variety of
backgrounds. These contributions have been in terms of strategies. One strategy
is the creation of an undergraduate mathematics student with little prior
knowledge of programming. Two other strategies were written by a 15 year old
secondary school student. As well as these strategy contributions, vital
architectural improvements to the library itself have also been received. You
can see an overview of the structure of the source code in
Figure~\ref{fig:overview}.
